The Lipid Interactome Repository

### 2025-01-14 LipidProbe/Sphingosine.qmd
minor tweaks
Testing embedded chem structures

---
title: "Trifunctional sphinganine"
---

@@

>>>>

---
title: "Trifunctional Sphingosine"
---

@@

:::{.callout collapse="true"}

#### Option 1: Static png

![](/LipidProbe/Structures/SphingosineStructure.png)

:::

:::{.callout collapse="true"}
#### Option 2: pubchem viewer embed

```{=html}
<iframe 
    src="https://pubchem.ncbi.nlm.nih.gov/compound/Sphingosine#section=3D-Conformer&fullscreen=true" 
    width="100%" 
    height="1000" 
    style="border:none;">
</iframe>

```
:::

(This might not be possible if the structure is not published to pubchem, there may be other options for embedding, but I don't know them right now)

### 2025-01-14 index.qmd
Testing embedded chem structures

A site map with big buttons leading to each of the lipid classes.

>>>>

```{=html}
<div style="text-align: center; margin: 20px;">
    <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
        <button style="background-color: #3498db; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Phosphatidic Acid
        </button>
    </a>
    <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
        <button style="background-color: #e74c3c; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Phosphatidylethanolamine
        </button>
    </a>
		<br>
		<a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
        <button style="background-color: #3277a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Diacylglycerol
        </button>
    </a>
		<br>
    <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Sphinganine
        </button>
    </a>
		<a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
        <button style="background-color: #eba434; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            Sphingosine
        </button>
    </a>

	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">
        <button style="background-color: #ba34eb; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            8-3 Fatty Acid
        </button>
    </a>

    <a href="LipidProbe/1-10_FattyAcid.qmd" style="text-decoration: none;">
        <button style="background-color: #a83260; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
            1-10 Fatty Acid
        </button>
    </a>
</div>
```
